$k$-Nearest Neighbour Search Using Space-filling Curves

### 2013-12-07 paper/paper.tex
Added intro bit

\begin{document}
\title{K Nearest Neighbour Search Using Space-filling Curves}
\author{Camara Lerner \hspace{2cm} Christopher Rabl \\
  Department of Mathematics and Computer Science \\
  University of Lethbridge, Canada}

@@

All methods of calculating K-Nearest Neighbours (KNN) are marred by the ``curse of dimensionality'' \cite{Bellman:2003}. Even though it is not an NP-Complete problem, it is still difficult to calculate KNN in high dimensions. Approaches such as spatially ordered trees (such as quadtrees and $kd$-trees) and space-filling curves have been applied to this problem in order to solve it more quickly than the naive approach (calculating a distance matrix between each point and choosing the smallest $k$ entries from the row corresponding to the query point $q$).

>>>>

\begin{document}
\title{$k$-Nearest Neighbour Search Using Space-filling Curves}
\author{Camara Lerner \hspace{2cm} Christopher Rabl \\
  Department of Mathematics and Computer Science \\
  University of Lethbridge, Canada}

@@

In the field of Machine Learning, the $k$-nearest neighbour problem is defined as follows: we are given a set of points $P = \left\{ {(v_i, c_i) : v_i \in \mathbb{R}^d, c_i \in C } \right\}$, where $C$ is a set of class labels (for instance, a binary class labeling would be: $C = \left\{ {0,1} \right\}$) and $v_i$ is a $d$-dimensional vector. The task at hand is, given a point $(q, c) \not \in P$, and where $c$ is unknown, attempt to assign a class label from $C$ the point based on the values of vectors that are close to $q$ in $P$. \\

All methods of calculating kNN are marred by the so-called ``curse of dimensionality'' \cite{Bellman:2003}. Even though it is not an NP-Complete problem, it is still difficult to calculate kNN in high dimensions since, if we assume that the algorithm is acting on $n$ $d$-dimensional points, the naive implementation takes $O(dn)$ time. Approaches such as spatially-ordered trees (such as quadtrees and $kd$-trees) and space-filling curves have been applied to this problem in order to solve it more quickly than the naive approach (calculating a distance matrix between each point and choosing the smallest $k$ entries from the row corresponding to the query point $q$).
